Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Make the figure/table numbers in bold #56
Add comments in the preamble

\usepackage{bigfoot} % Allow \verb in a footnote
\usepackage{cprotect} % Allow \verb in title
% Make figure captions left-aligned: see https://tex.stackexchange.com/questions/275131/align-caption-to-the-left
\usepackage{caption} 
\captionsetup{justification=raggedright,singlelinecheck=false}

>>>>

% Allow the use of \verb
\usepackage{bigfoot} % in a footnote
\usepackage{cprotect} % within the title{} / thanks{}: see https://ctan.org/tex-archive/macros/latex/contrib/cprotect?lang=en

% Make Figure X / Table X in Bold
\usepackage[labelfont=bf]{caption} % see https://tex.stackexchange.com/questions/32459/figure-how-to-have-figure-1-5-in-bold

% Make figure captions left-aligned (part of the caption package read above)
\captionsetup{justification=raggedright,singlelinecheck=false} % see https://tex.stackexchange.com/questions/275131/align-caption-to-the-left
